\Title

### 2016-02-21 manuscript/manuscript.tex
Add paragraph about the profiling

\begin{equation}
    d_i = f_i(\mathbf{p}),
\end{equation}

@@

The inversion method proposed here is implemented in the Python programming
language.
The software is freely available
under the terms of the BSD 3-clause open-source software license.
Our implementation relies on the open-source libraries
scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
and seaborn
\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks,
particularly for forward modeling using tesseroids.
We use the scipy.sparse package for sparse matrix arithmetic and linear
algebra.

@@

>>>>

\begin{equation}
    d_i = f_i(\mathbf{p}),
    \label{eq:forward}
\end{equation}

@@

The inversion method proposed here is implemented in the Python programming
language.
The software is freely available
under the terms of the BSD 3-clause open-source software license.
Our implementation relies on the open-source libraries
scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
and seaborn
\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks,
particularly for forward modeling using tesseroids.
We use the scipy.sparse package for sparse matrix arithmetic and linear
algebra.
The sparse linear system in Eq.~\ref{eq:gaussnewton-regul}
is solved using the conjugate gradient method implemented in scipy.sparse.

@@

We investigated the computation time spent in each section of the inversion
process using a source code profiler.
The profiler measures how much time is spent inside each function during
the execution of a program.
We ran the profiler on a single inversion of the training data set
using the estimated regularization parameter.
We tracked the total time spent inside each of the three functions
that represent the largest computational bottlenecks of the inversion:
solving the linear system in Eq.~\ref{eq:gaussnewton-regul}
using the conjugate gradient method,
performing the dot products required to compute
the Hessian matrix (Eq.~\ref{eq:hessian-regul})
and the gradient vector (Eq.~\ref{eq:gradient-regul}),
and forward modeling to calculate the predicted data (Eq.~\ref{eq:forward}).
The profiling results are presented in table~\ref{profiling}.
The time spent on forward modeling accounts for approximately
99.8\% of the total computation time.
